P.berghei pir analysis

### 2021-08-31 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Separate TPM calculation Rmd file

@@

Going to combine certain samples based on their distinctive profiles, e.g. <4h, 6-48h, >48h liver stages.

```{r combining_samples}
names_expt_tpms <- names(expt_tpms)

expt_tpms <- lapply(names(expt_tpms), function(expt){
  col_stage <- colnames(
    getElement(
      getElement(
        expt_tpms, 
        paste(expt)
      ),
      'tpm'
    )
  )

  liver_stage <- col_stage[
    str_detect(
      col_stage,
      pattern = 'Liv-[[:digit:]]{1,2}h'
    )
    ]

  new_liver_stage <- case_when(
    str_detect(liver_stage, pattern = 'Liv-(2|4)h') ~ 'Liv-pre4h',
    # str_detect(liver_stage, pattern = 'Liv-([5-9]|[1-3][0-9]|4[0-7])h') ~ 'Liv-pre47h',
    str_detect(liver_stage, pattern = 'Liv-(4[8-9]|[5-9][0-9])h') ~ 'Liv-post48h',
    TRUE ~ as.character(liver_stage),
  )

  if(length(new_liver_stage) > 0){
    new_liver_stage <-uniquify(new_liver_stage)
  }

  col_stage[
    str_detect(
      col_stage,
      pattern = 'Liv-[[:digit:]]{1,2}h'
    )
    ] <- new_liver_stage

  bloodmeal_stage <- col_stage[
    str_detect(
      col_stage, 
      pattern = 'BldMl-(1h|3h)_[[:digit:]]+'
    )
    ]

  bloodmeal_stage <- str_replace(
    bloodmeal_stage, 
    pattern = '(1h|3h)_[[:digit:]]+', 
    replacement = 'Pre3h'
  )
  if(length(bloodmeal_stage)>0){
    bloodmeal_stage <- uniquify(bloodmeal_stage)
  }

  col_stage[
    str_detect(
      col_stage, 
      pattern = 'BldMl-(1h|3h)_[[:digit:]]+'
    )
    ] <- bloodmeal_stage

  tpm_element <- getElement(
    getElement(
      expt_tpms, 
      paste(expt)
    ),
    'tpm'
  )

  colnames(tpm_element) <- col_stage

  list(tpm = tpm_element,
       experiment =   getElement(
         getElement(
           expt_tpms,
           paste(expt)
         ),
         'experiment'
       )
  )

})
names(expt_tpms) <- names_expt_tpms

#Re-ordering the list
expt_tpms <- (expt_tpms[order(names(expt_tpms))])
```

```{r remove_badly_clustering_samples}
expt_tpms$E08$tpm$`Liv-pre4h_1` <- NULL
expt_tpms$E03$tpm$`Asex-Schiz_1` <- NULL
expt_tpms$E03$tpm$`Asex-Schiz_3` <- NULL
```

```{r big_tpm}

```{r save_tpm}

write.csv()
```

>>>>

```{r remove_badly_clustering_samples}
berghei_tpm$`E08_Liv.pre4h_1` <- NULL
berghei_tpm$`E03_Asex.Schiz_1` <- NULL
berghei_tpm$`E03_Asex.Schiz_3` <- NULL
```

```{r save_tpm}
write.csv(berghei_tpm,
          'berghei_tpm.csv')
```

@@
